Plots for Latent Hawkes Paper

### 2020-10-18 output_scripts/Paper_Plots.Rmd
change potential fig 3b plot again

```{r}
ks_diff <-  (m2_ks - m1_ks)/m1_ks
ks_diff[is.nan(ks_diff)] <- 0
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks_diff))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
#order(as.vector(ks.stat.matrix),method = "")

@@

>>>>

```{r construct ks_diff}
ks_diff <-  (m2_ks - m1_ks)/m1_ks
ks_diff[is.nan(ks_diff)] <- 0
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks_diff))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
#order(as.vector(ks.stat.matrix),method = "")

@@

```{r construct ks diff normalised by num events}
norm_diff <- (m2_ks - m1_ks)/m1_ks
norm_diff[is.nan(norm_diff)] <- 0
count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)

for(i in expert_rank_10[[current_cohort]]) {
  for(j in expert_rank_10[[current_cohort]]) {
    if( norm_diff[i,j] != 0 ) {
      num_events <- unique_pairs_df %>% 
      filter(initiator == i & recipient == j) %>%
      pull(count)
      # diff[i,j] <- diff[i,j] / num_events
      count_mat[i,j] <- num_events
    }
  }
}

tibble(diff_norm = as.vector(norm_diff),
       events = as.vector(count_mat)) %>%
  filter(events > 0 ) %>%
  ggplot(aes(events,diff_norm)) + geom_point() +
  ylab("(M2-M1)/M1") +
  theme_minimal()

# # then same plot as above with diff
# col.vec <- cRamp(as.vector(diff))
# ## need to do some sort of transformation between these here
# vir_cols <- viridis::viridis(length((as.vector(diff))))
# #order(as.vector(ks.stat.matrix),method = "")
# 
# values <- as.vector(diff)
# sorted_vals <- sort(diff)
# #match(values,sorted_vals)
# col.vec.vir <- vir_cols[match(values,sorted_vals)]
# 
# ####
# par(oma = c(6,4,4,1), mar=rep(0,4),
#     mgp = c(0, .2, 0))
# layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
#                     byrow = TRUE),rep(12*12+1,12)), 
#        widths=c(rep(1,12),2), heights=rep(1,12))
# for(i in expert_rank_10[[current_cohort]]){
#   for(j in expert_rank_10[[current_cohort]]){
#     if(diff[i,j]==0){
#       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
#            axes = FALSE, frame=TRUE)
#       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
#            border = 0, col = 'white')
#     }else{
#       Lambda.test <- Lambda_matrix[i,j][[1]]
#       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
#             ylab="",xlab="",axes = FALSE, frame=TRUE)
#       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
#            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
#       # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
#       #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
#       # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
#       #      verticals = TRUE, col = "red", lwd = 2)
#     }
#   }
# }
# par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
# 
# col_obj <- list(x.vec = seq(min(as.vector(diff)),max(as.vector(diff)),
#                             length.out = 100),
#                 col.vec = viridis(100))
# 
# # temp <- cLegend(as.vector(ks_diff))
# 
# image(1, col_obj$x.vec,
#       matrix(data=col_obj$x.vec, 
#              ncol=length(col_obj$x.vec),nrow=1),
#       col=col_obj$col.vec,
#       xlab="",ylab="")
# # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
# #      cex.axis=2.4)
# 
# mtext(text=expert_rank_10[[current_cohort]], side=1,
#       line=1.8, outer=TRUE, cex=1.8,
#       at=1/14*c(1:12)-1/22)
# mtext(text = expert_rank_10[[current_cohort]],
#       side = 2, line = 0.5, outer = TRUE, cex = 1.8,
#       at =1/12*c(12:1)-1/20, las = 2)
# mtext(text = "M2-M1 normalised by num events", side = 3, line = 1.4, outer = TRUE,
#       cex = 2.2,
#       at=0.45, font=2)
